R Notebook

### 2020-03-17 datasets/data_preprocessing.nb.Rmd
- add nagtegaal dataset

# raw --------------------------------------------------------------------------

# asreview ---------------------------------------------------------------------

# remove missing abstracts 
final <- final[final$title != "NA", ]

# remove duplicates (171 duplicates)
final <- final %>%
  distinct(abstract, .keep_all = TRUE)
table(final$inclusion_code)

nrow(final)
final$abstract_included %>% table()
final$included %>% table()

# 
write.csv(final, "data/nagtegaal.csv")

@@

```{r}
nudging["test", ] <- c(1848, 382, 100)
```

@@

# add inclusion_code label 
w_asr$inclusion_code <- w_asr$label_abstract_screening + w_asr$label_included
w_asr$included <- w_asr$label_included
wilson["asreview", ] <- data_descr(w_asr)

```{r}
# create test dataset
w_test <- w_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  filter(abstract != "") %>%
  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts

@@

Statistics
```{r}
drops["wilson",] <- 
  w_asr %>%
   summarise(n = length(abstract),
                    na = sum(is.na(abstract)), # todo correct this, "NA", or ""
                    narate = sum(is.na(abstract))/length(abstract),
                    dup = sum(duplicated(abstract, incomparables = NA)),
                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract))

@@

       # test set 
       `candidates_test` =  nostudies(all, "test", "search"), 
       `fulltext_test` =  nostudies(all, "test", "ftext"), 
       `incl_test` =  nostudies(all, "test", "incl"), 
       `inclrate_test` = inclrate(all, "test")
       ) %>% 
  t() %>%
  kable("html") %>%
  kable_styling(full_width = TRUE) %>%
  #scroll_box(width = "100%", height = "200px") %>%
  pack_rows("Paper", 2, 5) %>%
  pack_rows("Raw data", 6, 9) %>%
  pack_rows("ASReview data", 10, 13) %>%
  pack_rows("Test data set", 14, 17)  
```

@@

# nagtegaal

>>>>

# raw --------------------------------------------------------------------------
n_raw <- read.csv("../../scripting/nagtegaal_preprocessing/data/output/nagtegaal.csv")
# asreview ---------------------------------------------------------------------

# remove missing abstracts 
nudging_test <- n_raw %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  filter(abstract != "", abstract != "NA") %>%
  distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
# missing statistics

@@

```{r}
nudging["test", ] <- data_descr(nudging_test)
```

@@

# add inclusion_code label 
w_asr$inclusion_code <- w_asr$label_abstract_screening + w_asr$label_included
w_asr$included <- w_asr$label_included
wilson["asreview", ] <- data_descr(w_asr)
```

```{r}
# create test dataset
w_test <- w_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  filter(abstract != "",
         abstract!= " ") %>%
  distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts

@@

Statistics
```{r}
drops["wilson", ] <- w_asr %>%
   summarise(n = length(abstract),
                    na = sum(is.na(abstract)), # todo correct this, "NA", or ""
                    narate = sum(is.na(abstract))/length(abstract),
                    dup = sum(duplicated(abstract, incomparables = NA)),
                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract))

@@

       # test set 
       `candidates_test` =  nostudies(all, "test", "search"), 
       `fulltext_test` =  nostudies(all, "test", "ftext"), 
       `incl_test` =  nostudies(all, "test", "incl"), 
       `inclrate_test` = inclrate(all, "test")) %>% 
  t() %>% 
  kable("html") %>%
  kable_styling(full_width = TRUE) %>%
  #scroll_box(width = "100%", height = "200px") %>%
  pack_rows("Paper", 2, 5) %>%
  pack_rows("Raw data", 6, 9) %>%
  pack_rows("ASReview data", 10, 13) %>%
  pack_rows("Test data set", 14, 17)  
```

@@

# nudging 
write.csv(nudging_test, "test_datasets/nudging.csv")
